Public Gender Egalitarianism: A Dataset of Dynamic Comparative Public Opinion Toward Egalitarian Gender Roles in the Public Sphere

### 2020-12-28 paper/dcpo_gender_roles.Rmd
add abstract

abstract: ""
keywords: "gender inequality, public opinion, measurement"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
spacing: double
bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), "s.bib$", recursive = TRUE))`}
# csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
---

@@

Collective attitudes toward the appropriate roles of women and men in society---whether labeled culture or ideology or public opinion---constitute one of the primary explanations for women's exclusion from political power and policy influence [see, e.g., @Yates2017, 103-104; @Paxton2021, 113-114].
Yet even a half century after @RuleKrauss1974 [, 1719] called in the pages of the _APSR_ for more and better data on these collective attitudes, what we have available to us remains inadequate for fully examining their causes and consequences.
In the decades since, national and cross-national surveys have included a plethora of relevant questions, but sustained focus has been scant and the variety of these survey items renders the resulting data incomparable.
As a consequence, cross-national research has been constrained to study countries at just one or a few time points [see, e.g., @Paxton2003; @Alexander2012; @Ruedin2012; @Glas2020] or to rely on proxies such as predominant religion or the percentage of women in office [see, e.g., @Burns2001, 340-341; @Claveria2014; @Barnes2018].
Broadly cross-national and longitudinal investigation of, for example, the argument that such "attitudes influence both the supply of, and demand for, female candidates" has remained a topic for future research [@Paxton2010, 47].

>>>>

abstract: "Societal attitudes toward gender roles in education, the workplace, and politics play a central part in theorizing on the difficulty women face in achieving political equality, but shortcomings in the available data have prevented direct examination of many implications of these theories. Drawing on recent advances in latent variable modeling of public opinion and a comprehensive collection of survey data, we present the Public Gender Egalitarianism dataset to address this need: comparable estimates of the public's attitudes on gender equality in the public sphere across more than one hundred countries over time. These PGE scores are strongly correlated with responses to single survey items as well as with measures of women's rates of participation in the labor force and on corporate boards. We expect that the PGE data will become an invaluable source for broadly cross-national and longitudinal research on the causes and consequences of collective attitudes toward gender equality in the public sphere."
keywords: "gender inequality, public opinion, measurement"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
spacing: double
bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), "s.bib$", recursive = TRUE))`}
# csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
---

@@

Collective attitudes toward the appropriate roles of women and men in society---whether labeled culture or ideology or public opinion---constitute one of the primary explanations for women's exclusion from political power and policy influence [see, e.g., @Yates2017, 103-104; @Paxton2021, 113-114].
Yet even a half century after @RuleKrauss1974 [, 1719] called in the pages of the _APSR_ for more and better data on these collective attitudes, what we have available to us remains inadequate for fully examining their causes and consequences.
In the decades since, national and cross-national surveys have included a plethora of relevant questions, but sustained focus has been scant and the variety of these survey items renders the resulting data incomparable.
As a consequence, cross-national research has been constrained to study countries at just one or a few time points [see, e.g., @Paxton2003; @Alexander2012; @Ruedin2012; @Glas2020] or to rely on proxies such as predominant religion or the percentage of women in office [see, e.g., @Burns2001, 340-341; @Claveria2014; @Barnes2018].
Cross-national and longitudinal investigation of, for example, the argument that such "attitudes influence both the supply of, and demand for, female candidates" has remained a topic for future research [@Paxton2010, 47].
